%-------------------------
% Resume in Latex
% Author : Ojas Srivastava
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape [Name LastName]} \\ \vspace{1pt}
    \small [phone] $|$ \href{mailto:ojas@knowojas.com}{[email@email.com]} $|$ 
    \href{https://linkedin.com/in/0jas0jas}{linkedin.com/in/[linkedin]} $|$
    \href{https://knowojas.com/}{[personal website]} $|$
    \href{https://github.com/0jas0jas}{github.com/[github]}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Canadian Uni}{Canada}
      {Bachelor of Science in Mathematics and Computer Science}{Aug. 2023 -- May. 2027}
  \resumeSubHeadingListEnd
      \textbf{Relevant Coursework}{: Algorithms and Data Structures (Java), Software Design (Java), Programming Languages and Paradigms (OCaml), Software Systems (C, Bash), Computer Systems (MIPS Assembly), Compiler Design, Theory of Computation, Statistics (R), Probability, Numerical Analysis (MATLAB), Abstract Algebra I \& II, Ordinary Differential Equations, Advanced Calculus, Operating Systems (C/C++, Linux)}

 %-----------Certs-----------
%-----------Certs - Ultra Compact-----------
\section{Certifications}
\textbf{\hspace{5pt} Cisco Certified Network Associate (CCNA)} \hfill \textit{In Progress}\vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Software Development Intern $|$ \textnormal{VueJs, WCAG, Java (SpringBoot), MySQL} }{Apr. 2025 -- Aug. 2025}
    {\href{https://nakisa.com}{[Mid size B2B]} | Full-time}{Montréal, QC}
    \resumeItemListStart
      \resumeItem{Enhanced accessibility features across 5+ web applications for 10+ fortune 500 companies.}
      \resumeItem{Optimized keyboard navigation and screen reader support, reducing navigation time by 30\%.}
      \resumeItem{Conducted accessibility audits with Axe and Lighthouse, resolving 50+ critical issues.}
      \resumeItem{Collaborated with UX and frontend teams to implement high-contrast themes and ARIA attributes.}
      \resumeItem{Engineered 3+ Java backend services, fixing 20+ database bugs and improving query performance by 40\%.}
      \resumeItem{Resolved 40+ critical export and frontend bugs, improving system reliability by 25\%.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Developer $|$ \textnormal{React JS, GraphQL, PostgresSQL, C/C++, Python} }{Mar. 2023 -- Apr. 2025}
    {\href{https://codeday.org}{[Big non-profit]} | Full-time}{Remote/ Seattle, WA}
    \resumeItemListStart
      \resumeItem{Developed and maintained Next.js frontend with GraphQL API integration, reducing page load times by 30\%.}
      \resumeItem{Engineered PostgreSQL backend with automated pipelines, cutting workflows by 40\% and processing 10,000+ records daily.}
      \resumeItem{Created 8+ automation tools in Python and C++, saving 20+ hours weekly and improving efficiency by 25\%.}
      \resumeItem{Led a global team of 15 to deliver hackathons for 1,000+ participants annually.}
    \resumeItemListEnd

\resumeSubheading
  {Software Development Intern $|$ \textnormal{Next.js, Python, Git, React, AWS}}{Jan. 2024 -- Jun. 2024}
  {[Small college] | Full-time}{[location]}
  \resumeItemListStart
    \resumeItem{Led complete website redesign with faculty, boosting UI/UX and WCAG accessibility for 2,000+ students.}
    \resumeItem{Engineered Python backend + database refactor, cutting staff query time 60\% via optimized PostgreSQL access.}
    \resumeItem{Deployed and hosted the redesigned platform on AWS (EC2/S3), ensuring reliable uptime for 2,000+ students.}
    \resumeItem{Trained 200+ students across 20+ workshops on Next.js/React/Git, launching 50+ student projects.}
  \resumeItemListEnd



  % \resumeSubheading
  %   {Developer}{Jan. 2024 -- Present}
  %   {Hack4Impact}{Montréal, QC}
  %   \resumeItemListStart
  %     \resumeItem{Spearheaded a team of 5 in full-stack development projects benefiting three non-profit organizations.}
  %     \resumeItem{Engineered software solutions that impacted 50,000+ individuals in underrepresented communities.}
  %     \resumeItem{Boosted online engagement for partner organizations by 40\%.}
  %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects \href{https://knowojas.com/projects}{\small\textit{(more at [personal website])}}}
    \resumeSubHeadingListStart

\resumeProjectHeading
    {\href{https://nuclearapp.ca}{\textbf{[startup] (AI-Powered Notetaking Startup)}} $|$ Next.js, Supabase, Prisma, Redis, PyTorch}{Jun. 2025}
    \resumeItemListStart
      \resumeItem{Co-founded an AI-powered notetaking app with 100+ active users, driving 40\% monthly user growth and processing 500+ notes daily.}
      \resumeItem{Trained a transformer-based classification model on 50,000+ handwritten and typed notes, delivering personalized, context-aware recommendations per student.}
      \resumeItem{Built end-to-end ML pipeline covering data preprocessing, training, evaluation, and inference via a FastAPI backend.}
      \resumeItem{Implemented semantic search with vector embeddings using Perplexity Sonar, cutting retrieval time by 60\% and achieving 95\% accuracy.}
    \resumeItemListEnd




  \resumeProjectHeading
    {\href{https://github.com/0jas0jas/symlang}{\textbf{SymLang (McHacks Winner)}} $|$ JavaScript, Next.js, TensorFlow.js, Computer Vision}{Feb. 2025}
    \resumeItemListStart
      \resumeItem{Created AI-powered gesture recognition system for hands-free programming, achieving 90\% accuracy across 15+ gestures.}
      \resumeItem{Trained custom classification model in TensorFlow.js, achieving 85\% accuracy with 10,000+ training samples.}
      \resumeItem{Showcased at McHacks 2025, demonstrating an innovative approach to accessibility and intuitive coding.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/0jas0jas/codeview}{\textbf{CodeView (UoFT Hacks winner)}} $|$ Next.js, Tesseract React, Docker, PostgreSQL, Prisma}{Jan. 2025}
    \resumeItemListStart
      \resumeItem{Created code analysis app that scans handwritten code and provides Big O complexity analysis for students.}
      \resumeItem{Implemented OCR technology using Tesseract.js to scan handwritten code with 90\% accuracy and real-time Big O analysis.}
      \resumeItem{Built a comprehensive rating system that evaluates code efficiency and provides actionable feedback to improve student coding skills.}
    \resumeItemListEnd


    
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript/TypeScript, Python, C/C++, OCaml} \\
     \textbf{Technologies}{: React, Next.js, FastAPI, PostgreSQL, MongoDB, Docker, Git, PyTorch, Three.js}
    }}
\end{itemize}


% \resumeProjectHeading
%     {\href{https://github.com/0jas0jas}{\textbf{CachyOS}} $|$ C/C++, Bash, Linux Kernel, Arch Packaging}{2025 -- Present}
%     \resumeItemListStart
%       \resumeItem{Contributed bug fixes, optimizations, and packaging scripts to CachyOS (Arch-based distro); merged PRs improving kernel scheduler performance by 15\% for gaming workloads.}
%       \resumeItem{Developed custom KDE tweaks and performance patches used by 10k+ users.}
%     \resumeItemListEnd




  % \resumeProjectHeading
  %   {\textbf{LiteraLingo} $|$ React, Docker, PostgreSQL, Prisma}{Aug. 2024}
  %   \resumeItemListStart
  %     \resumeItem{Built an educational app with Hack4Impact to help autistic children learn English.}
  %     \resumeItem{Leveraged React for UI, Prisma for database management, and Docker for deployment.}
  %     \resumeItem{Crafted adaptive exercises tailored for neurodiverse learners.}
  %   \resumeItemListEnd

  % \resumeProjectHeading
  %   {\textbf{Sheep in Sheep’s Clothing} $|$ C\#, Unity}{Jan. 2025}
  %   \resumeItemListStart
  %     \resumeItem{Constructed a stealth-based puzzle game for McGameJam 2025, focusing on innovative gameplay mechanics.}
  %     \resumeItem{Leveraged Unity for game development and C\# for scripting, creating a polished player experience.}
  %     \resumeItem{Collaborated with a team of 8 on level design, character art, and AI behaviors.}
  %   \resumeItemListEnd

  % \resumeProjectHeading
  %   {\textbf{McMayhem} $|$ Godot, GDScript}{Jan. 2024}
  %   \resumeItemListStart
  %     \resumeItem{Executed a 48-hour GameJam with a 3-member team, reconfiguring 10+ 3D models.}
  %     \resumeItem{Ranked in the top 5 out of 50 entries.}
  %   \resumeItemListEnd

  % \resumeProjectHeading
  %   {\textbf{Mon Cahier} $|$ Go, JavaScript, Hugo}{May. 2023}
  %   \resumeItemListStart
  %     \resumeItem{Created a blog on computer science and mathematics, attracting 1,000+ monthly readers.}
  %     \resumeItem{Published 15+ articles in McGill University’s The Abstract magazine.}
  %     \resumeItem{Deployed the site with Go and Hugo, maintaining 99.9\% uptime.}
  %   \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
