%-------------------------
% Resume in Latex
% Author : Ojas Srivastava
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ojas Srivastava} \\ \vspace{1pt}
    \small (514) 237-7035 $|$ \href{mailto:ojas@knowojas.com}{ojas@knowojas.com} $|$ 
    \href{https://linkedin.com/in/0jas0jas}{linkedin.com/in/0jas0jas} $|$
    \href{https://knowojas.com/}{knowojas.com} $|$
    \href{https://github.com/0jas0jas}{github.com/0jas0jas}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McGill University}{Montréal, QC}
      {Bachelor of Science in Mathematics and Computer Science}{Aug. 2023 -- May. 2027}
  \resumeSubHeadingListEnd
      \textbf{Relevant Coursework}{: Algorithms \& Data Structures, Software Design, Operating Systems, Compiler Design, Theory of Computation, Software Systems, Programming Languages \& Paradigms}
      
 %-----------Certs-----------
%-----------Certs - Ultra Compact-----------
\section{Certifications}
\textbf{\hspace{5pt} Cisco Certified Network Associate (CCNA)} \hfill \textit{In Progress}\vspace{-8pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Software Development Intern $|$ \textnormal{Vue.js, WCAG, Java (Spring Boot), MySQL} }{Apr. 2025 -- Aug. 2025}
    {\href{https://nakisa.com}{Nakisa} | Full-time}{Montréal, QC}
    \resumeItemListStart
      \resumeItem{Engineered accessibility across multiple web apps used by enterprise clients, strengthening keyboard and screen reader support.}
      \resumeItem{Conducted accessibility audits with Axe and Lighthouse and resolved critical WCAG issues.}
      \resumeItem{Built Java backend services and fixed database bugs, improving query performance and system reliability.}
      \resumeItem{Partnered with UX and frontend teams to implement high-contrast themes and ARIA improvements.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Developer $|$ \textnormal{React, GraphQL, PostgreSQL, C/C++, Python} }{Mar. 2023 -- Apr. 2025}
    {\href{https://codeday.org}{CodeDay} | Full-time}{Remote / Seattle, WA}
    \resumeItemListStart
      \resumeItem{Developed and maintained a Next.js frontend with GraphQL API integration, improving page load times.}
      \resumeItem{Built PostgreSQL backend pipelines that processed large daily record volumes and streamlined internal workflows.}
      \resumeItem{Created Python and C++ automation tools that saved significant manual work each week.}
      \resumeItem{Led a global team delivering hackathons for over 1,000 participants annually.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Development Intern $|$ \textnormal{Next.js, Python, Git, React, AWS}}{Jan. 2024 -- Jun. 2024}
    {MMPG College | Full-time}{Kalakankar, India}
    \resumeItemListStart
      \resumeItem{Led a full website redesign that improved UI/UX and accessibility for students and faculty.}
      \resumeItem{Refactored the Python backend and PostgreSQL access layer to reduce staff query time.}
      \resumeItem{Deployed the platform on AWS for reliable hosting and improved site availability.}
      \resumeItem{Trained students through workshops on Next.js, React, and Git, helping launch new projects.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  % \resumeSubheading
  %   {Developer}{Jan. 2024 -- Present}
  %   {Hack4Impact}{Montréal, QC}
  %   \resumeItemListStart
  %     \resumeItem{Spearheaded a team of 5 in full-stack development projects benefiting three non-profit organizations.}
  %     \resumeItem{Engineered software solutions that impacted 50,000+ individuals in underrepresented communities.}
  %     \resumeItem{Boosted online engagement for partner organizations by 40\%.}
  %   \resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects \href{https://knowojas.com/projects}{\small\textit{(more at knowojas.com)}}}
    \resumeSubHeadingListStart

    \resumeProjectHeading
    {\href{https://github.com/CachyOS/linux-cachyos}{\textbf{CachyOS Linux Distribution (Open-Source Contributor)}} $|$ Linux Kernel, C, Bash, Git, Docker}{Ongoing, 2025}
\resumeItemListStart
  \resumeItem{Contributed optimizations to CachyOS, improving kernel performance and package build scripts for better stability in dev environments.}
  \resumeItem{Developed Bash automation tools and Docker configs to streamline kernel compilation and testing, reducing build times by 25\% on my local setup.}
  \resumeItem{Submitted PRs for web-facing docs and Arch package maintenance, enhancing usability for developers deploying cloud-native apps like AWS/Docker stacks.}
\resumeItemListEnd

\resumeProjectHeading
    {\href{https://nuclearapp.ca}{\textbf{Nuclear (AI-Powered Notetaking Startup)}} $|$ Next.js, Supabase, Prisma, Redis, PyTorch}{Jun. 2025}
    \resumeItemListStart
      \resumeItem{Co-founded an AI-powered notetaking app with 100+ active users, driving 40\% monthly user growth and 500+ notes processed daily.}
      \resumeItem{Trained a transformer-based model on 50,000+ handwritten and typed notes to generate personalized study recommendations.}
      \resumeItem{Built the ML pipeline for preprocessing, training, evaluation, and inference through a FastAPI backend.}
      \resumeItem{Implemented semantic search with vector embeddings using Perplexity Sonar, cutting retrieval time by 60\% and reaching 95\% accuracy.}
    \resumeItemListEnd



\resumeProjectHeading
    {\href{https://github.com/0jas0jas/symlang}{\textbf{SymLang (McHacks Winner)}} $|$ JavaScript, Next.js, TensorFlow.js, Computer Vision}{Feb. 2025}
    \resumeItemListStart
      \resumeItem{Built an AI-powered gesture recognition system for hands-free programming, reaching 90\% accuracy across 15+ gestures.}
      \resumeItem{Trained a TensorFlow.js classification model on 10,000+ samples to support real-time gesture input.}
      \resumeItem{Showcased the project at McHacks 2025 as an accessibility-focused coding interface.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/0jas0jas/codeview}{\textbf{CodeView (UofT Hacks Winner)}} $|$ Next.js, Tesseract.js, Docker, PostgreSQL, Prisma}{Jan. 2025}
    \resumeItemListStart
      \resumeItem{Built an app that scans handwritten code and generates Big-O complexity analysis for students.}
      \resumeItem{Implemented OCR with Tesseract.js, achieving 90\% scan accuracy and real-time analysis.}
      \resumeItem{Added a feedback system that rates code efficiency and suggests improvements.}
    \resumeItemListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript/TypeScript, Python, C++, OCaml} \\
     \textbf{Technologies}{: React, Next.js, FastAPI, PostgreSQL, MongoDB, Docker, Git, PyTorch, Three.js}
    }}
\end{itemize}


% \resumeProjectHeading
%     {\href{https://github.com/0jas0jas}{\textbf{CachyOS}} $|$ C/C++, Bash, Linux Kernel, Arch Packaging}{2025 -- Present}
%     \resumeItemListStart
%       \resumeItem{Contributed bug fixes, optimizations, and packaging scripts to CachyOS (Arch-based distro); merged PRs improving kernel scheduler performance by 15\% for gaming workloads.}
%       \resumeItem{Developed custom KDE tweaks and performance patches used by 10k+ users.}
%     \resumeItemListEnd




  % \resumeProjectHeading
  %   {\textbf{LiteraLingo} $|$ React, Docker, PostgreSQL, Prisma}{Aug. 2024}
  %   \resumeItemListStart
  %     \resumeItem{Built an educational app with Hack4Impact to help autistic children learn English.}
  %     \resumeItem{Leveraged React for UI, Prisma for database management, and Docker for deployment.}
  %     \resumeItem{Crafted adaptive exercises tailored for neurodiverse learners.}
  %   \resumeItemListEnd

  % \resumeProjectHeading
  %   {\textbf{Sheep in Sheep’s Clothing} $|$ C\#, Unity}{Jan. 2025}
  %   \resumeItemListStart
  %     \resumeItem{Constructed a stealth-based puzzle game for McGameJam 2025, focusing on innovative gameplay mechanics.}
  %     \resumeItem{Leveraged Unity for game development and C\# for scripting, creating a polished player experience.}
  %     \resumeItem{Collaborated with a team of 8 on level design, character art, and AI behaviors.}
  %   \resumeItemListEnd

  % \resumeProjectHeading
  %   {\textbf{McMayhem} $|$ Godot, GDScript}{Jan. 2024}
  %   \resumeItemListStart
  %     \resumeItem{Executed a 48-hour GameJam with a 3-member team, reconfiguring 10+ 3D models.}
  %     \resumeItem{Ranked in the top 5 out of 50 entries.}
  %   \resumeItemListEnd

  % \resumeProjectHeading
  %   {\textbf{Mon Cahier} $|$ Go, JavaScript, Hugo}{May. 2023}
  %   \resumeItemListStart
  %     \resumeItem{Created a blog on computer science and mathematics, attracting 1,000+ monthly readers.}
  %     \resumeItem{Published 15+ articles in McGill University’s The Abstract magazine.}
  %     \resumeItem{Deployed the site with Go and Hugo, maintaining 99.9\% uptime.}
  %   \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
