%-------------------------
% Game Dev Resume in Latex
% Author: Ojas Srivastava
% Based off of: https://github.com/sb2nov/resume [attached_file:1]
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ojas Srivastava} \\ \vspace{1pt}
    \small 514-237-7035 $|$ \href{mailto:ojas@knowojas.com}{ojas@knowojas.com} $|$ 
    \href{https://linkedin.com/in/0jas0jas}{linkedin.com/in/0jas0jas} $|$
    \href{https://knowojas.com/}{knowojas.com} $|$
    \href{https://github.com/0jas0jas}{github.com/0jas0jas}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, GDScript, JavaScript/TypeScript, Python, C++, Java, OCaml} \\
     \textbf{Game Engines \& Frameworks}{: Unity (C\#), Godot (GDScript), Next.js, React, Tailwind CSS, Three.js} \\
     \textbf{Tools \& Libraries}{: Git/GitHub, Docker, TensorFlow.js, PyTorch, Tesseract.js, PostgreSQL, Prisma} \\
     \textbf{Game Dev Focus}{: Gameplay mechanics, AI behaviors, level design, 3D modeling, Computer Vision, Gesture Recognition}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McGill University}{Montréal, QC}
      {Bachelor of Science in Mathematics and Computer Science}{Aug. 2023 -- May. 2027}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Algorithms and Data Structures (Java), Software Systems (C/Bash), Computer Systems (MIPS), Compiler Design, Theory of Computation, Operating Systems (C/C++, Linux)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {Software Development Intern $|$ \textnormal{Vue.js, Java (Spring Boot), MySQL} }{Apr. 2025 -- Aug. 2025}
      {\href{https://nakisa.com}{Nakisa} | Full-time}{Montréal, QC}
      \resumeItemListStart
        \resumeItem{Engineered 3+ Java backend services and fixed 20+ bugs, improving reliability by 25\% -- transferable to game server optimization.}
        \resumeItem{Resolved 40+ frontend bugs, enhancing UX principles applicable to game interfaces.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer $|$ \textnormal{Next.js, GraphQL, PostgreSQL, C/C++, Python} }{Mar. 2023 -- Apr. 2025}
      {\href{https://codeday.org}{CodeDay} | Full-time}{Remote/ Seattle, WA}
      \resumeItemListStart
        \resumeItem{Led global team of 15 delivering hackathons for 1,000+ participants, coordinating game dev workshops and tech stacks.}
        \resumeItem{Developed 8+ automation tools in Python/C++ for game jam workflows, saving 20+ hours weekly.}
        \resumeItem{Built Next.js frontend with GraphQL, optimizing load times by 30\% for event platforms.}
      \resumeItemListEnd



    \resumeSubheading
      {Web Development Intern $|$ \textnormal{Next.js, Python}}{Jan. 2024 -- Jun. 2024}
      {MMPG College | Full-time}{Kalakankar, India}
      \resumeItemListStart
        \resumeItem{Redesigned college website and taught 20+ web dev sessions, building collaborative skills for game teams.}
        \resumeItem{Refactored student database for staff access, honing data management for game backends.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://github.com/0jas0jas/symlang}{\textbf{SymLang (McHacks Winner)}} $|$ Next.js, TensorFlow.js, Computer Vision}{Feb. 2025}
      \resumeItemListStart
        \resumeItem{Built AI gesture recognition for hands-free programming (90\% accuracy on 15+ gestures), adaptable to VR/AR game controls.}
        \resumeItem{Trained TensorFlow.js model on 10,000+ samples, showcasing real-time AI integration.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Sheep in Sheep’s Clothing} $|$ C\#, Unity}{Jan. 2025}
      \resumeItemListStart
        \resumeItem{Developed stealth puzzle game for McGameJam 2025 with innovative mechanics, AI, and level design.}
        \resumeItem{Collaborated with team of 8 on characters, behaviors, and polished Unity deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{McMayhem} $|$ Godot, GDScript}{Jan. 2024}
      \resumeItemListStart
        \resumeItem{48-hour GameJam entry (top 5/50): Reconfigured 10+ 3D models for fast-paced action game.}
        \resumeItem{Led 3-person team in rapid prototyping and deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://github.com/0jas0jas/codeview}{\textbf{CodeView (UofT Hacks Winner)}} $|$ Next.js, Tesseract.js, Docker, PostgreSQL}{Jan. 2025}
      \resumeItemListStart
        \resumeItem{OCR app scans handwritten code for Big O analysis (90\% accuracy), useful for game scripting tools.}
        \resumeItem{Built rating system with feedback for code efficiency.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Nuclear (AI Notetaking)} $|$ Next.js, Supabase, Prisma, Redis}{Jun. 2025}
      \resumeItemListStart
        \resumeItem{Co-founded app with 100+ users; custom AI models for semantic search (95\% accuracy, 60\% faster retrieval).}
        \resumeItem{Secured 3 educational partnerships; skills in scalable AI applicable to game NPCs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
