%-------------------------
% Equipment Person Resume (Fixed) - McGill Athletics
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------SPACING FIXES----------
\setlength{\parsep}{0pt}
\setlength{\parskip}{1pt}
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

% Fixed custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{ #4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ojas Srivastava} \\ \vspace{1pt}
    \small (514) 237-7035 $|$ \href{mailto:ojas@knowojas.com}{ojas@knowojas.com} $|$ 
    Montréal, QC $|$ Valid Driver's License $|$ Available Tue-Fri 3-11:15pm, Sat 1-9:15pm
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
Reliable McGill student with 2+ years hands-on experience in equipment setup/teardown, venue preparation, inventory control, and customer service for high-traffic events (1,000+ attendees). Physically capable (lifting 50+ lbs), mechanically adept, bilingual (English/French functional). Ready for Currie Gymnasium operations including evening shifts, facility maintenance, and emergency response.

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Operations}: Equipment distribution/setup, venue preparation, inventory tracking, minor repairs \\
     \textbf{Physical}: Lift 100+ lbs, drive for deliveries, use hand trucks/platform lifts, handle hazardous materials \\
     \textbf{Service}: Client verification, policy enforcement, lost/found management, public interaction \\
     \textbf{Languages}: English (functional spoken/written), French (functional spoken/written) \\
     \textbf{Other}: Mechanical aptitude, visual inspections, emergency procedures, evening availability
    }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {McGill University}{Montréal, QC}
  {B.Sc. Mathematics \& Computer Science (Expected 2027)}{Aug. 2023 -- Present}
\resumeItemListStart
  \resumeItem{High School Leaving Diploma; experienced in physical labor and facility operations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Equipment \& Logistics Coordinator}{Montréal, QC / Remote}
  {McGill Hackathons \& CodeDay Events}{2023 -- 2025}
\resumeItemListStart
  \resumeItem{Set up/teardown equipment for 5+ events serving 1,000+ participants (projectors, computers, furniture).}
  \resumeItem{Managed inventory distribution/return, tracked overdue items, conducted daily equipment inspections.}
  \resumeItem{Performed minor repairs/troubleshooting on tech equipment; handled deliveries and venue prep.}
  \resumeItem{Coordinated with service providers for repairs; enforced event policies with participants.}
\resumeItemListEnd

\resumeSubheading
  {Venue Operations Volunteer}{Montréal, QC}
  {Peel Cinema Club (McGill University)}{2023 -- 2025}
\resumeItemListStart
  \resumeItem{Prepared screening venues: equipment setup (projectors/sound), seating arrangements, cleanup.}
  \resumeItem{Distributed supplies/equipment to 50+ attendees per event; managed lost/found items.}
  \resumeItem{Conducted facility walkthroughs, reported maintenance issues, assisted with emergency procedures.}
  \resumeItem{Handled laundry/cleaning of event materials post-screening.}
\resumeItemListEnd

\resumeSubheading
  {Event Logistics Coordinator}{Goa, India}
  {International Film Festival of India}{Nov. 2022}
\resumeItemListStart
  \resumeItem{Set up venues for panels/symposia: moved furniture/equipment using carts/hand trucks.}
  \resumeItem{Verified attendee access, distributed materials, liaised with external vendors for repairs.}
  \resumeItem{Managed high-volume deliveries and inventory during peak festival operations.}
\resumeItemListEnd



\end{document}
