%-------------------------
% Cover Letter in Latex
% Author : Ojas Srivastava
%------------------------

\documentclass[11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\begin{document}

%----------HEADING----------
\begin{flushleft}
    {\Large \textbf{Ojas Srivastava}} \\[4pt]
    (514) 237-7035 \quad \href{mailto:ojas@knowojas.com}{ojas@knowojas.com} \quad
    \href{https://linkedin.com/in/0jas0jas}{linkedin.com/in/0jas0jas} \quad
    \href{https://github.com/0jas0jas}{github.com/0jas0jas}
\end{flushleft}

\vspace{6pt}
April 9, 2026

\vspace{12pt}
Hiring Team \\
L3Harris Technologies \\
Ottawa, ON

\vspace{12pt}
\textbf{Re: Embedded Software Engineering Intern (Job Code 35767)}

\vspace{12pt}
Dear Hiring Team,

I am writing to apply for the Embedded Software Engineering Intern position at L3Harris in Ottawa. The role sits exactly at the intersection of systems-level C/C++ development, Linux, and real-world algorithmic problem-solving --- areas I have been building depth in through both professional experience and open-source work. More than that, L3Harris's mission of connecting critical domains in the interest of national security is the kind of work I want my skills to matter for.

My most direct preparation for this role is my ongoing contributions to \href{https://github.com/0jas0jas}{CachyOS}, an Arch-based Linux distribution. Working at the kernel level, I have diagnosed and fixed low-level software issues, written Bash automation scripts for packaging workflows, and merged performance patches that improved the Linux kernel scheduler by 15\% for real-time workloads --- changes now running on machines used by 10,000+ users. This is exactly the kind of independent technical research and careful debugging under-the-hood that I understand embedded software development demands.

At CodeDay, I designed and built 8+ automation tools in C++ and Python that reduced manual engineering work by 20+ hours per week. I also debugged and resolved performance bottlenecks across a production stack, which taught me to read through system behaviour methodically rather than making assumptions. At Nakisa, I resolved 50+ critical defects across enterprise software used by Fortune 500 clients, working closely with systems and product teams to meet deadlines without cutting corners.

My coursework at McGill reinforces this hands-on experience: I have completed Operating Systems (C/C++ and Linux), Software Systems (C and Bash), and Computer Systems (MIPS Assembly), all of which give me the low-level mental model that embedded work requires.

I am eligible to work in Canada and willing to relocate to Ottawa for the term. I understand the role requires eligibility for the Controlled Goods Program and a government security clearance, and I am fully prepared to pursue those.

I would welcome the opportunity to speak with your team about how my background fits the work L3Harris is doing. Thank you for your time and consideration.

\vspace{18pt}
Sincerely,

\vspace{24pt}
\textbf{Ojas Srivastava}

\end{document}
